### 2021-02-23 introduction.tex
uvod

Certain orderings help to make superposition a decision procedure on certain fragments of first-order logic 
(see, e.g., \cite{DBLP:conf/lics/GanzingerN99,DBLP:conf/cade/HustadtKS05}).
It is also well known that giving the highest precedence to the predicate symbols introduced as names 
during the Tseitin transformation % of the input formula 
\cite{Tseitin1983} can immediately make saturation produce the exponential 
set of clauses that the transformation is designed to avoid \cite{Reger2016}.
%
However, the precise way by which the choice of a precedence 
influences the follow-up proof search on a general problem is extremely hard to predict. % indirect

@@

In this work,

\newpage

@@

% CITE us: co tehdy, co ted!

@@

\iffalse % AWR draft

>>>>

It is well known that giving the highest precedence to the predicate symbols introduced as names 
during the Tseitin transformation % of the input formula 
\cite{Tseitin1983} can immediately make saturation produce the exponential 
set of clauses that the transformation is designed to avoid \cite{Reger2016}.
Also, certain orderings help to make superposition a decision procedure on certain fragments of first-order logic 
(see, e.g., \cite{DBLP:conf/lics/GanzingerN99,DBLP:conf/cade/HustadtKS05}).
However, the precise way by which the choice of a precedence 
influences the follow-up proof search on a general problem is extremely hard to predict. % indirect

@@

In this work, we propose a machine learning system that learns to predict for an ATP
whether one precedence is going to lead to a faster proof search on a given problem than another.
Given a previously unseen problem, it can then be asked to recommend the best possible precedence for an ATP to run with.
Relying only on the logical structure of the problems, % for the learning, 
the system generalizes the knowledge about favourable precedences across problems with different signatures.

Our recommender uses a graph convolutional neural network \cite{kipf2017semisupervised}
to represent the problem structure. It learns from the ATP performance on selected problems
and \emph{pairs of randomly sampled} precedences. This information is then used to train
a \emph{symbol cost model}, which realizes the recommendation by simply sorting 
the problem's symbols according the obtained costs.

This work strictly improves on our previous experiments with linear regression models and simple hand-crafted symbol features \cite{DBLP:conf/cade/Bartek020}
and is, to the best of our knowledge, a first method able to propose good symbol precedences automatically 
using a non-linear transformation of the input problem structure.

The rest of this paper is organized as follows. \ldots
% explicit contributions (mixed with ``as follows'')?

\todo{Asi bych znovu (po abstraktu) nerikal, kolik nam vyjde. Spis jen ze sekce ta a ta je to tom, ze se tam evaluu s vampirem na TPTP. }
When coupled with the ATP Vampire and trained on problems from the TPTP library,
the recommender improves on the state-of-the art general-purpose precedence generating scheme
\texttt{invfreq} by more than \SI{4}{\percent}.

@@

\iffalse

@@

% \iffalse % AWR draft

### 2021-02-23 main.tex
Comment out appendix
Add an idea for future work
uvod

@@

\appendix
\input{appendix}

>>>>

Thorough analysis of the model: how does it work? how does it generalize?

Besides tackling the particular task of generating symbol precedences,
the approach described in \cref{sec:architecture} may be of a more general interest
for a researcher trying to apply statistical learning to produce arbitrarily long permutations
that optimize some non-differentiable quantitative criterion.
\todo{FB: Give examples of such tasks. How about constructive TSP?}

@@

%\appendix
%\input{appendix}
